Adopting agile in the large: motivations, success factors and challenges

### 2014-05-04 journal/article.tex
Possible addition
Misunderstanding

@@

% Misunderstandings in the agile model

>>>>

% Include quotation?
% * Some teams mirrored waterfall approaches in their behavior --> Did not work
% [P32]
% Then comes execution and the learning really begins. Teams’ working habits
% determine their success.  Often teams quickly ignore plans in favor of using
% tactical approaches that mirror waterfall thinking. This contrasts nicely with
% those more attuned to applying agile.

@@

In some cases the misunderstanding of the agile model was described as ``doing
mini waterfalls'' [P6]. Managers were using Scrum terminology, but at the same
time committing unreasonable workloads on teams [P6]. In another case a
waterfall nature was seen in giving task estimates as hours left, and task
breakdowns disconnected from what was really being done [P27].
